%-------------------------
% Resume in LaTeX
% Author : Duncan Gibbs
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% only for pdflatex
% \input{glyphtounicode}
% \pdfgentounicode=1

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

\usepackage{pagecolor,lipsum}
\definecolor{background-color}{HTML}{3B3F45}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{0.08}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

\newcommand*{\fontdir}[1][fonts/]{\def\@fontdir{#1}}
\fontdir

\usepackage{fontspec}
\setmainfont[
    Path=\@fontdir,
    UprightFont=*-400-Book,
    ItalicFont=*-400-BookItalic,
    BoldFont=*-700-Bold,
    BoldItalicFont=*-700-BoldItalic
]{Jost}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{black} {\titlerule[2pt]} \vspace{-4pt}]

%---COMMANDS---
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubHeading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeEducation}[3]{
    \begin{tabularx}{0.8\textwidth}{X X X}
        \textbf{#1} & \textit{#2} & \textit{#3}
    \end{tabularx}
    \vspace{-4pt}
}

\newcommand{\resumeReferences}[3]{
    \begin{center}
        \setlength\tabcolsep{20pt}
        \begin{tabular}{l c r}
            #1 & #2 & #3
        \end{tabular}
    \end{center}
}

\newcommand{\reference}[3]{
    \begin{tabular}{c}
        \textbf{#1} \\
        \textit{\color{dark-grey}#2} \\
        \texttt{#3}
    \end{tabular}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%---RESUME---

\begin{document}
\pagecolor{white}

%---HEADING---
\begin{flushleft}
    \textbf{\Huge DUNCAN GIBBS} \\ \vspace{7pt}
    \small \faGithub \hspace{1pt} \texttt{duncgibbs} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{1pt} \texttt{duncgibbs@gmail.com} \hspace{1pt} $|$ 
    \hspace{1pt} \faPhone \hspace{1pt} \texttt{913.314.1021}
    \\ \vspace{-1pt}
\end{flushleft}

%---EXPERIENCE---
\section{EXPERIENCE}
    \resumeSubHeadingListStart

        \resumeSubHeading
            {Sparq}{October 2021 -- Present}
            {Senior Consultant}{Remote / Oklahoma City, OK}
            \resumeItemListStart
                \resumeItem{Acted as Technical Architect, Lead Developer, DevOps Engineer, and DB Admin in the course of my consultancy. }
                \resumeItem{Led a small team in developing multiple GCP based Ruby on Rails applications for a biomedical technology company.}
                \resumeItem{Worked with clients, project managers, and salespeople in order to negotiate contracts, define Statements of Work, and staff multiple projects.}
                \resumeItem{Interviewed, onboarded, and managed developers for both my company and clients.}
            \resumeItemListEnd

        \resumeSubHeading
            {Tailwind}{July 2019 -- September 2021}
            {Platform Engineer}{Oklahoma City, OK / Remote}
            \resumeItemListStart
                \resumeItem{Designed and implemented new fullstack features and upgrades on both modern React and legacy PHP apps.}
                \resumeItem{Migrated existing pieces of our application to and created novel serverless AWS microservices using CloudFormation.}
                \resumeItem{Built internal tools for our Engineering and Operations teams using AWS, TypeScript, and React/Next.}
            \resumeItemListEnd

        \resumeSubHeading
            {Torch.AI}{April 2017 -- July 2019}
            {Senior Software Engineer \& Technical Architect}{Leawood, KS / Washington, DC}
            \resumeItemListStart
                \resumeItem{Developed a physics based node graph using three.js and D3.js for visualizing and analyzing networks and supply chains.}
                \resumeItem{Created and pitched techincal solutions to clients, including a queue-worker, a realtime notification service, a file parser, and other microservices.}
                \resumeItem{Promoted to manager of an external, cross-organizational Agile team for the DoD NBIS program, including presenting to, and working with stakeholders in DC and KC.}
            \resumeItemListEnd

        \resumeSubHeading
            {Red Nova Labs}{March 2016 -- April 2017}
            {Software Engineer}{Westwood, KS}
            \resumeItemListStart
                \resumeItem{Designed and developed new features, fixed bugs, and optimized code in a multi-tier, multi-language web application.}
                \resumeItem{Directed the effort, in conjunction with Operations, to communicate with clients to find and fix bugs in our software.}
                \resumeItem{Onboarded new developers and maintained a wiki of guides.}
                \resumeItem{Excelled in annual, internal, self-driven hackathons.}
            \resumeItemListEnd

    \resumeSubHeadingListEnd

%---SKILLS---
\section{SKILLS}
    \begin{itemize}[leftmargin=0in, label={}]
        {
            \item{
                \textbf{Languages} {: Node, JavaScript, TypeScript, Rust, C\#, Ruby, PHP, Python, Bash, Java, Haskell}\vspace{4pt} \\
                \textbf{Web} {: HTML(5), CSS(3), Sass, Less, React, Next.js, Rails(7), Chakra UI, Material UI, Ant Design, Laravel, Django, Express, Wordpress}\vspace{4pt} \\
                \textbf{Databases} {: PostgreSQL, MySQL, DynamoDB, MongoDB, ArangoDB, Aurora}\vspace{4pt} \\
                \textbf{Tools} {: Unix, Git, AWS, GCP, Jupyter, Docker, Kubernetes, Unity, Photoshop, Lightroom, MS Office}
            }
        }
    \end{itemize}

%---EDUCATION---
\section{EDUCATION}
    \resumeEducation
        {Hendrix College}
        {Computer Science}
        {Conway, AR}

%---REFERENCES---
\section{REFERENCES}
    \resumeReferences
        {
            \reference
                {Andres Barbaro}
                {Tailwind}
                {405.694.3438}
        }
        {
            \reference
                {Will Washburn}
                {Tailwind}
                {508.558.1931}
        }
        {
            \reference
                {Jon Kramer}
                {Torch.AI}
                {913.526.4745}
        }

%-------------------------------------------
\end{document}
